\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-08-10 tex/gitlinks.tex
setup azure

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/fe12fa16a5cc76c1ba72d97241fb9545da144edf/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/fe12fa16a5cc76c1ba72d97241fb9545da144edf/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/fe12fa16a5cc76c1ba72d97241fb9545da144edf/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/user/repo/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/e5ab316138ff452eef773701f33097cf0c53c3a9/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/e5ab316138ff452eef773701f33097cf0c53c3a9/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/e5ab316138ff452eef773701f33097cf0c53c3a9/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}
